Redshift evolution of the underlying type Ia supernova stretch distribution

### 2021-04-29 Nicolas.tex
Added proof and  corrected refs, signed copright form

\institute{Univ Lyon, Univ Claude Bernard Lyon 1, CNRS, IP2I Lyon / IN2P3, IMR
    5822, F-69622, Villeurbanne, France
    \and 
    Université Clermont Auvergne, CNRS/IN2P3, Laboratoire de
    Physique de Clermont, F-63000 Clermont-Ferrand, France.
    \and
    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720 
    \and
    Institut fur Physik, Humboldt-Universität zu Berlin, Newtonstr. 15,
    12489 Berlin
    \and
    University of Southampton: Southampton, GB
}

\date{Submitted to A\&A\ the 19th of May 2020}

@@

\bibitem[Brout et al.(2019)]{brout2019} Brout, D., Scolnic, D., Kessler, R., et
al.\ 2019, \apj, 874, 150

@@

\bibitem[Jones et al.(2018)]{jones2018} Jones, D.~O., Riess, A.~G., Scolnic,
D.~M., et al.\ 2018, \apj, 867, 108

\bibitem[Jones et al.(2018)b]{jones2018b} Jones, D.~O., Scolnic, D.~M., Riess,
A.~G., et al.\ 2018, \apj, 857, 51

@@

\bibitem[Saunders et al.(2018)]{saunders2018} Saunders, C., Aldering, G.,
Antilogus, P., et al.\ 2018, \apj, 869, 167. doi:10.3847/1538-4357/aaec7e

@@

\bibitem[Strolger et al.(2004)]{strolger04} Strolger, L.-G., Riess, A.~G.,

>>>>

\institute{Univ Lyon, Univ Claude Bernard Lyon 1, CNRS, IP2I Lyon / IN2P3, IMR
    5822, F-69622, Villeurbanne, France
    \and 
    Université Clermont Auvergne, CNRS/IN2P3, Laboratoire de
    Physique de Clermont, F-63000 Clermont-Ferrand, France
    \and
    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720, USA
    \and
    Institut fur Physik, Humboldt-Universität zu Berlin, Newtonstr. 15,
    12489 Berlin, Germany
    \and
    University of Southampton, Southampton, UK
}

\date{Submitted to A\&A\ the 19th of May 2020 / Accepted 26 February 2021}

@@

@@

@@

@@

\bibitem[Strolger et al.(2004)]{strolger04} Strolger, L.-G., Riess, A.~G., et
al.\ 2004, \apj, 613, 200
